---
title: "d3r: Data-Driven Documents (D3) in R Ecosystem"
output: github_document
---

## Introduction

<div style="display: flex; align-items: center;">
  <img src="https://upload.wikimedia.org/wikipedia/commons/1/15/Logo_D3.svg" style="height: 150px; margin-right: 10px;">
  <img src="https://upload.wikimedia.org/wikipedia/commons/1/1b/R_logo.svg" style="height: 150px;">
</div>

d3r is an R package designed to seamlessly integrate D3.js into your R environment, enabling dynamic and interactive data visualizations. Whether you're working in RStudio, Shiny, Quarto, Jupyter, Selenium, or plain HTML, d3r provides an easy way to create, embed, and interact with D3.js-based charts, graphs, and visualizations without needing deep JavaScript knowledge.

# Installation

``` {r, eval = FALSE}
devtools::install_github("JacekPardyak/d3r", upgrade = "never")
```

## Usage

In these usage examples, we use `Selenium` mode to take screenshots of documents generated by D3.js. Check the `tests` folder for additional live examples in different modes.

```{r}
library(d3r)
'// Set SVG dimensions
const width = 400, height = 300;

// Create SVG inside the div
const svg = d3.select("#container")
  .append("svg")
  .attr("width", width)
  .attr("height", height);

// Append a circle
svg.append("circle")
  .attr("cx", 200)  // X position
  .attr("cy", 150)  // Y position
  .attr("r", 50)    // Radius
  .attr("fill", "steelblue");  // Color
'  |> make(title = "D3.js in R", mode = "selenium")  |> knitr::include_graphics()
```


